Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-12 ms.tex
explain origin of CO Krj km/s to Kcmb conversion factors
get rid of outdated comments/notes to self
reference FWHM values listed in table rather than redundantly listing them in the text itself

\subsection{Smoothing}
\label{sec:smth}
For our full-resolution model, we wish to simultaneously fit \verb|i100| along 
with the four highest-frequency \PLANCK~bands. To properly combine these maps, 
they must have the same point spread function (PSF). \verb|i100|, with its 
$6.1'$ symmetric Gaussian beam, has the lowest angular resolution of the 
relevant maps. To match PSFs, we have therefore smoothed each of the 
\PLANCK~maps under consideration to \verb|i100| resolution by considering each 
native \PLANCK~map to have a symmetric Gaussian beam and smoothing by the 
appropriate symmetric Gaussian such that the resulting map has a  $6.1'$ FWHM. 
The FWHM we assign to the native \PLANCK~maps is taken from \cite{planckbeam}, 
specifically $5.01'$ for 217 GHz, $4.86'$ for 353 GHz, $4.84'$ for 545 GHz, and
 $4.63'$ for 857 GHz.

@@

Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ in \PLANCK~band 
$\nu_i$ due to the CO transition from J=$N$ to J=$(N$$-$1). $I_3$ represents 
the Type 3 CO amplitude in  K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. The 
$F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
$K_{CMB}$ for particular band/transition pairs. The relevant values adopted 
are:

\noindent
$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$$K_{CMB}/K_{RJ}$,

\noindent
$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$$K_{CMB}/K_{RJ}$, and

\noindent
$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$$K_{CMB}/K_{RJ}$.

@@

% need to cite reference for K_rj -> K_cmb conversion factors

@@

%mention that all of this assumes that residual CMB dipole
% and other low order-corrections are negligible at 857 GHz

% Maybe it's not necessary to mention the 545 GHz check ... although
% i should do the check eventually as to whether choosing 545 GHz
% for the absolute zero point is consistent with choosing 857 GHz
% to within the errors that i'm quoting

%We also repeated the full-sky FDS99 prediction versus \PLANCK~regression at 
%545 GHz. After

%We also repeated the full-sky and quadrant regressions with the FDS99 
%predictions at 545 GHz (see bottom panel of Figure XX). We find the 
%slopes vary from XX to YY with an rms scatter of ZZ. The 545 GHz zero points
%have an rms scatter of SS, which is consistent with the 545 GHz zero 
%point rms implied by the scatter in 857 GHz zero point.

@@

In the course of this study we use not only \PLANCK~857 GHz, but also all of
the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
absolute zero level offsets that must be applied to each of the five
lowest-frequency \PLANCK~bands, we perform a regression versus the 
\PLANCK~857 GHz map corrected for the absolute zero level offset derived in
 $\S$\ref{sec:zp_abs}. We assume no offset need be applied
to \verb|i100|, which has a zero level tied to H\,\textsc{i} by SFD.
% maybe need to restate the idea that we're deriving zero points by assuming
% that the band of interest must approach zero linearly as the reference
% (in this case 857 ghz) approaches zero.

@@

\begin{equation}
\label{eqn:source}
S_{\nu} = \frac{f_1q_1(\nu/\nu_0)^{\beta_1}B_{\nu}(T_1) + f_2q_2(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)}{f_1q_1(\nu/\nu_0)^{\beta_1}+f_2q_2(\nu/\nu_0)^{\beta_2}}
\end{equation}
%basically just finish clarifying here that we want to start simple by fitting
%only two parameters for each pixel since we only have 5 intensity
% measurements per pixel in our baseline fits at 6.1 arcmin resolution

>>>>

\subsection{Smoothing}
\label{sec:smth}
For our full-resolution model, we wish to simultaneously fit \verb|i100| along 
with the four highest-frequency \PLANCK~bands. To properly combine these maps, 
they must have the same point spread function (PSF). \verb|i100|, with its 
$6.1'$ symmetric Gaussian beam, has the lowest angular resolution of the 
relevant maps. To match PSFs, we have therefore smoothed each of the 
\PLANCK~maps under consideration to \verb|i100| resolution by considering each 
native \PLANCK~map to have a symmetric Gaussian beam and smoothing by the 
appropriate symmetric Gaussian such that the resulting map has a  $6.1'$ FWHM. 
The FWHM values we assign to the native \PLANCK~maps are taken from 
\cite{planckbeam}, and are listed in Table \ref{table:offs}.

@@

Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ in \PLANCK~band 
$\nu_i$ due to the CO transition from J=$N$ to J=$(N$$-$1). $I_3$ represents 
the Type 3 CO amplitude in  K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. The 
$F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
$K_{CMB}$ for particular band/transition pairs. The relevant values, 
calculated with the \textit{Unit Conversion and Colour Correction} software 
utilities (\verb|v1.2|), are:

\noindent
$F_{12CO, 100, 1, 0}$=1.478$\times$10$^{-5}$$K_{CMB}/(K_{RJ} \ km/s)$,

\noindent
$F_{12CO, 217, 2, 1}$=4.585$\times$$10^{-5}$$K_{CMB}/(K_{RJ} \ km/s)$, and

\noindent
$F_{12CO, 353, 3, 2}$=1.751$\times$$10^{-4}$$K_{CMB}/(K_{RJ} \ km/s)$.

@@

% might consider quoting rounder values in text, most precise values are:
% 100 GHz, J=1->0 : 1.478e-5, 217 GHz, J=2->1 : 4.585e-5, 
% 353 GHz, J=3->2 : 1.751e-4

@@

% mention that all of this assumes that residual CMB dipole
% and other low order-corrections are negligible at 857 GHz

@@

In the course of this study we use not only \PLANCK~857 GHz, but also all of
the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
absolute zero level offsets that must be applied to each of the five
lowest-frequency \PLANCK~bands, we perform a regression versus the 
\PLANCK~857 GHz map corrected for the absolute zero level offset derived in
 $\S$\ref{sec:zp_abs}. We assume no offset need be applied
to \verb|i100|, which has a zero level tied to H\,\textsc{i} by SFD.

@@

\begin{equation}
\label{eqn:source}
S_{\nu} = \frac{f_1q_1(\nu/\nu_0)^{\beta_1}B_{\nu}(T_1) + f_2q_2(\nu/\nu_0)^{\beta_2}B_{\nu}(T_2)}{f_1q_1(\nu/\nu_0)^{\beta_1}+f_2q_2(\nu/\nu_0)^{\beta_2}}
\end{equation}
